### 2023-03-05 tex/article.tex
Change Chl-a for textit
I feel it is more appropriate ?
like emph is emphasis, it is a different thing

\subsubsection{Quantification of the impact of fronts on Chl-\emph{a}}

@@

\subsubsection{Local impact of fronts on Chl-\emph{a}}

@@

\subsubsection{Biome-scale impact of fronts on Chl-\emph{a}}

>>>>

\subsubsection{Quantification of the impact of fronts on Chl-\textit{a}}

@@

\subsubsection{Local impact of fronts on Chl-\textit{a}}

@@

\subsubsection{Biome-scale impact of fronts on Chl-\textit{a}}
